### 2025-01-15 short/sections/summary.tex
Update summary.tex

\textcolor{black}{I am a post-doctoral researcher in Computational Social Science at the Institute of Public Administration at the Faculty of Governance and Global Affairs at Leiden University, Netherlands. I hold a DPhil (PhD) in Politics from the University of Oxford, United Kingdom. Before my DPhil, I earned an MA (1st) in Political Science and a BA (2:1) in Government, both from the Universidad de Chile.}

\textcolor{black}{My research interests lie in the intersection of comparative politics and government, focusing mainly on cabinets, political regimes and civil services. Methodologically, my interests rely on the application of quantitative text analysis, machine learning methods and causal inference strategies in the comparative politics field. In the last years, my work has been published in {\itshape The International Journal of Press/Politics}, {\itshape World Development}, {\itshape Government and Opposition}, {\itshape The British Journal of Politics and International Relations}, {\itshape Bulletin of Latin American Research} and elsewhere.}

\textcolor{black}{During my post-doctorate at Leiden, I am working on two research projects funded by the Dutch Research Council (NWO) related to how the rule of law has changed over time and automated text analysis of investment data to study the effects of governance on sustainable investments. Specifically, I employ Natural Language Processing (NLP) and text-as-data techniques to find patterns and topics within big text data.}
\vspace{1mm}
\end{cvparagraph}

>>>>

\textcolor{black}{I am a post-doctoral researcher in Computational Social Science at the Institute of Public Administration, Faculty of Governance and Global Affairs, Leiden University, the Netherlands. I hold a DPhil (PhD) in Politics from the University of Oxford, UK, and prior to that, I completed an MA (1st) in Political Science and a BA (2:1) in Government at the Universidad de Chile.}

\textcolor{black}{My research, which initially focused on comparative politics and government, particularly cabinets, political regimes and civil services, has now expanded to explore the emerging field of digital governance and other policy domains. My work has appeared in {\itshape Social Science Computer Review}, {\itshape World Development}, {\itshape Government and Opposition}, {\itshape The International Journal of Press/Politics}, {\itshape The British Journal of Politics} and elsewhere.}

\textcolor{black}{During my current postdoctoral appointment, I am mainly contributing to an NWO-funded project on automated text analysis of investment data, investigating how governance structures shape sustainable investments. Specifically, I use Natural Language Processing (NLP) and text-as-data methods to identify patterns and topics within large-scale textual corpora. In addition, I teach the Institutions of Governance and Development course at Leiden University College.}
\vspace{1mm}
\end{cvparagraph}
